---
title: "DataViz Makeover 1"
description: |
  Below is the submission for the DataViz Makeover 1.
author:
  - name: Louis Chong Jia Jun (louis.chong.2019@mitb.smu.edu.sg)
    url: https://www.linkedin.com/in/louis-chong-jia-jun
date: 01-19-2021
output:
  distill::distill_article:
    self_contained: false
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# 1.0 Critiques of Data Visualisation

This is bad. When the data is large, both in terms of the number of observations and the number of variables, [Corrgram](http://www.datavis.ca/papers/corrgram.pdf) tend to be used to visually explore and analyse the structure and the patterns of relations among variables.

## Clarity

- Good
- Bad
- Okay

## Aesthetics

- Good
- Bad
- Okay

First, you will learn how to create correlation matrix using [*pairs()*](https://www.rdocumentation.org/packages/graphics/versions/3.6.0/topics/pairs) of R Graphics.  Next, you will learn how to plot corrgram using **corrplot** package of R.


# 2.0 Improvements to Current Design

## Clarity

- Good
- Bad
- Okay

## Aesthetics

- Good
- Bad
- Okay

## Sketch of Proposed Design

Insert image

- Good
- Bad
- Okay


# 3.0 Step-by-Step Description of Data Visualisation Preparation

- Data source, import into Tableau
- Data preparation, cleaning
- Create new calculated field, parameter
- Sheet 1, sheet 2, create charts
- Tooltips, details, formatting
- Dashboard, title


# 4.0 Proposed Data Visualisation Using Tableau

Insert image

```{r, echo=FALSE, message=FALSE, layout="l-body-outset", fig.width=12, fig.height=6}
fa <- ggplot(data=wine, aes(x= `fixed acidity`)) +
  geom_histogram(bins=20, color="black", fill="light blue")
va <- ggplot(data=wine, aes(x= `volatile acidity`)) +
  geom_histogram(bins=20, color="black", fill="light blue")
ca <- ggplot(data=wine, aes(x= `citric acid`)) +
  geom_histogram(bins=20, color="black", fill="light blue")
rs <- ggplot(data=wine, aes(x= `residual sugar`)) +
  geom_histogram(bins=20, color="black", fill="light blue")
ch <- ggplot(data=wine, aes(x= `chlorides`)) +
  geom_histogram(bins=20, color="black", fill="light blue")
fSO2 <- ggplot(data=wine, aes(x= `free sulfur dioxide`)) +
  geom_histogram(bins=20, color="black", fill="light blue")
tSO2 <- ggplot(data=wine, aes(x= `total sulfur dioxide`)) +
  geom_histogram(bins=20, color="black", fill="light blue")
density <- ggplot(data=wine, aes(x= density)) +
  geom_histogram(bins=20, color="black", fill="light blue")
pH <- ggplot(data=wine, aes(x= pH)) +
  geom_histogram(bins=20, color="black", fill="light blue")
sulphates <- ggplot(data=wine, aes(x= sulphates)) +
  geom_histogram(bins=20, color="black", fill="light blue")
alcohol <- ggplot(data=wine, aes(x= alcohol)) +
  geom_histogram(bins=20, color="black", fill="light blue")

ggarrange(fa, va, ca, rs, ch, fSO2, tSO2, density, pH, sulphates, alcohol, 
          ncol = 4, nrow = 3)
```


## Major Observations

- Good
- Good
- Good